\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Clean up new style problem
that I introduced in ce120dbdeda19583a1525694f88898775129a572
Smoothing out wording in Sec 8 a little bit.  Elaborating on what we mean by smart automation.

\section{Recommendations}
\label{sec:recommendations}
Our design resulted in shorter connection times and greater success,  but it could still be improved. We do not recommend our exact design as the optimal design, although we believe it is an improvement. Instead, we offer some suggestions based on what we learned: \\

@@

We did not try any designs that asked for user inputs, due to design constraints. But we see further room for improvement in success rate, connection time, and configuration time that could be made by leveraging user input and automation. Here, we talk about the potential approaches to redesigning the interface:  \\

\begin{itemize}
\item{\bfseries Design changes:} as demonstrated by our design iteration, tweaks in the interface can result in significant usability improvements.
\item{\bfseries Naive automation:} a scheme that chooses bridges, waits for timeouts, and tries another bridge so users do not need to do this themselves. We call this ``naive'' automation, because this scheme does not leverage information about the user or network conditions and essentially just automates the trial and error process that users would otherwise have to do manually. 
\item{\bfseries Smart automation:} a scheme that connects to a hard-to-censor bridge, which then automatically assigns a bridge that works for the user based on availability and bandwidth constraints. We call this ``smart'' automation because this scheme involves communication with Tor servers, which choose a bridge that will work for the user on the first try. 
\end{itemize}

>>>>

\section{Recommendations}
\label{sec:recommendations}
Our design resulted in shorter connection times and greater success rates,  but it could still be improved. We do not recommend our exact design as the optimal design, although we believe it is an improvement. Instead, we offer some suggestions based on what we learned: \\

@@

We did not try any designs that asked for user inputs, due to design constraints. But we see further room for improvement in success rate, connection time, and configuration time that could be made by leveraging user input and automation. We see several promising approaches to improving the Tor launcher:  \\

\begin{itemize}
\item{\bfseries Design changes:} as demonstrated by our design iteration, incremental improvements to the interface can result in significant usability improvements.
\item{\bfseries Naive automation:} the launcher could automatically choose a bridges, wait for timeout, and try another bridge on failure, so users do not need to do this themselves. We call this ``naive'' automation, because this scheme does not leverage information about the user or network conditions and essentially just automates the trial and error process that users would otherwise have to do manually. 
\item{\bfseries Smart automation:} the launcher could initially connect to Tor via a hard-to-censor bridge, then contact a central server (over this Tor connection) to identify a bridge that will work for the user based on availability and bandwidth constraints, automatically choose that bridge, and re-connect to Tor using that bridge. We call this ``smart'' automation because this scheme involves communication with Tor servers, which choose a bridge that will work for the user on the first try. 
\end{itemize}
